\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\setlength{\parskip}{\smallskipamount}
\setlength{\parindent}{0pt}


\makeatletter


\providecommand{\tabularnewline}{\\}


\makeatother


\chapter{Summary}


This dissertation outlines a generic search for supersymmetric particles in compressed scenarios. The search is performed with proton-proton collisions at $\sqrt{s} = 13$ TeV and the CMS detector using the full Run II dataset with integrated luminosity of 138 fb$^{-1}$. A generic compressed SUSY topology is identified as ISR recoiling against an energetic invisible and soft visible system. This topology is organized into a set of decay trees by labeling topological components as either part of the ISR or Sparticle systems. The sparticle system is further subdivided into a di-sparticle system with visible and invisble components partitioned into each. The decay tree reference frames are approximated using a rule set from the Recursive Jigsaw Reconstruction framework that guides the optimal partitioning for each refrence frame. Following the construction of each event's decay tree, kinematic mass sensitive variables are derived to discriminate against backgrounds. Each event is then further categorized in bins of the mass sensitive kinematic variables $R_{ISR}$ and $M_\perp$ as well as physics objects combinatorics such as lepton multiplicity, jet multiplicity, b-tagging, and other complementary variables. The organization of all categories and the optimization of those categories has been discussed where the multitude of different complementary regions act as cross constraints for the fit. The lepton selection is also defined and the efficiencies of that selection are modeled with the Tag-and-Probe method. The Tag-and-Probe measurements are used to  model and correct systematic effects through scale factors for each component of the Gold, Silver, and Bronze in each year separately. The Tag-and-Probe scale factors adn systematics are a minor contribution to the overall fit which is composed of over 200 nuisance parameters. The nuisance parameters were derived by studying control region fits and statistical metrics such as the Poisson likelihood, z-score, or chi-squared. The set of nuisances is found to be satisfactory in describing both the control region fit and the validation region fit. But, the set of nuisances have been studied to have few enough degrees of freedom to not reject a signal hypothesis in an signal injected fit. From the establishment of this fit, expected limits are shown for T2tt, T2bW, TChiWZ, TChipmWW, and TSlepSlep  which extend the current exclusion threshold significantly.   

